The Cluster Difference Imaging Photometric Survey (CDIPS). I. Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-06-10 paper/ms.tex
wrote an abstract

\shortauthors{Bouma et al.}
\shorttitle{CDIPS I: Method \& Sectors 6--8}

@@

@@

\title{
  The Cluster Difference Imaging Photometric Survey (CDIPS).
  I. Method, Light Curves, and Planet Candidates from Sectors 6--8
}

@@

\begin{abstract}
  Lorem ipsum.
\end{abstract}

>>>>

\shortauthors{Bouma et al.}
\shorttitle{CDIPS I: Method, Sectors 6 \& 7}

@@

% BEGIN NUMBERS
\newcommand{\numberpcs}{10\ }
\newcommand{\numberlcs}{42{,}424\ }
\newcommand{\numberclusters}{424\ }

@@

\title{
  The Cluster Difference Imaging Photometric Survey (CDIPS).  I.
  Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7
}

@@

\begin{abstract}
  % Context
  The Transiting Exoplanet Survey Satellite (TESS) has begun to
  photometrically monitor almost every nearby star cluster in
  the Galaxy.
  % Aims
  As part of the CDIPS project, we have begun processing the TESS
  full-frame images to make high-precision light curves for candidate
  members of stellar associations, moving groups, and open clusters.
  %
  Our eventual hope is to discover giant transiting planets, and probe
  the exoplanet size and separation distributions for planets younger
  than 1 Gyr.
  %
  For this study, we made \numberlcs light curves of candidate young
  stars in \numberclusters clusters.
  Each light curve repesents between 20 and 25 days of observations
  of a star brighter than $G_{Rp}=16$, sampled at 30 minute cadence.
  % Methods
  We describe in detail the image subtraction and light curve
  processing techniques we used to create the light curves, which
  have noise properties in-line with theoretical expectations.
  % Results
  We then highlight the \numberpcs planet candidates identified from
  an initial search, describe the vetting procedures that they have
  survived, and emphasize the need for additional
  spectroscopic and photometric observations.
  %
  We also comment on the possible use of the light curve sample for
  studies of stellar rotation evolution, and binary eccentricity
  damping.
  %
  The data products include both the light curves and also vetting
  reports, all of which are available at
  \url{archive.stsci.edu/prepds/cdips}.
\end{abstract}
